HMMotion: Using tracking data to predict coverage strategies in American Football

### 2024-12-31 submission.Rmd
.

@@

We locally decoded this sequence.

This probabilistic approach allows us to infer dynamic coverage patterns during plays with pre-snap motion. To exploit this high-dimensional time-series data, we calculate the entropy of the state probabilities, thus, producing measures of uncertainty for each play.

#### 3. Post-motion prediction
We re-train the pre-motion model to predict whether the defense plays a man- or zone coverage scheme, however, in this step, we incorporate results from the HMM analysis as further covariates. In particular, we use the aforementioned state probabilities of guarding the different offensive players in each second.

To remediate this, we derive the decision of man- or zone coverage from the number of switches for individual players. In particular, a low number of switches when offensive players are in motion indicates man coverage whereas a higher number indicates zone coverage.

Entropie

>>>>

This probabilistic approach allows us to infer dynamic coverage patterns during plays with pre-snap motion.

@@

#### 3. Post-motion prediction
We re-train the pre-motion model to predict whether the defense plays a man- or zone coverage scheme, but, in this step, we incorporate results from the HMM analysis as further covariates. However, a caveat of the aforemententioned state probabilities is that they constitute as high-dimensional time-series data which makes them hard to use them as covariates. An outlet of this problem is to employ suitable summary statistics (`r colorize("Robert hier spezifizieren welche du final genommen hast","orange")`). In particular, we calculate for each defender the most likely offensive player in each time point $t$ and count the number of state switches. Summing these numbers across defenders and, thus, plays, are the first, relatively simple, summary statistic. In addition to that, we calculate the mean entropy during a play:

$$H(X) = - \sum_{i=1}^n P(x_i) \log_b P(x_i)$$
Entropy is a measure of uncertainty or randomness in a probability distribution, here, the probability distribution of the defender for guarding the offensive players. Higher entropy indicates greater unpredictability, while lower entropy signifies more predictability.

In particular, we use the aforementioned state probabilities of guarding the different offensive players in each second. To exploit this high-dimensional time-series data, we calculate the entropy of the state probabilities, thus, producing measures of uncertainty for each play.
